Designing a Search for the BBC

### 2014-02-06 paper.tex
Added abstract; replaced "I" with "the authors"; and abbreviation "section" as "Sect." where appropriate.

\begin{abstract}

\end{abstract}

@@

The purpose of this report is to start the high-level design -- and perhaps
look at the lower levels of one or two aspects -- of a search application
specific to BBC content. The intent is to provide a consistent user interface
that allows the audience to find news articles, sport results,
TV catch-up, education resources and everything else the BBC produces.

@@

Checkland and Scoles \citep{checkland1990soft} decribed a \emph{Rich Picture} approach
for representing a problem situation early in SSM approaches.
Given the size and complexity of the
search system as a whole, a useful initial step is to create such an informal
representation of what is known about the problem. Figure~\ref{rich-picture}
shows what I know of the audience, search and most BBC online content areas.
Note that not all areas are covered and a strong emphasis is placed on TV
catch-up (e.g. via the iPlayer product). Radio catch-up is not mentioned
as it shares a lot of similarity with television in terms of use and any
differences are out of scope for this design.

@@

The problem of
a BBC-wide search application was predicted --
and has certainly shown itself -- to be a very large-scale problem, the
full extent of which cannot be covered in this report. Thus it
is reasonable to conclude that the problem is not yet solved
at every level, but the high-level solutions are certainly promising.

@@

Overall, we have some promising, high-level models from which to
start making such more fine-grained decisions about the search
application. The use cases are likely sufficient for early iterations
or a \emph{Minimal Viable Product} \citep{junk2000dynamic} and
the behaviours capture the overall needs of the system. There is still
much scope for returning to our systems thinking and Soft Systems
Methodology to monitor the general model for Checkland's ``3 Es''
(efficacy, efficiency and effectiveness) \citep{checkland1990soft},
which is only briefly touched on in my attempts to relate the
data model to the user's interaction with the system.

@@

Even the models that are presented in this report do not paint the full
picture, but it could be argued that it is not their purpose to do so.
As stated at the end of section~\ref{appraisal}, the use case diagram
provides a starting point that might be sufficient for an early
iteration of a project in an \emph{Agile} methodology. \citep{beck2001agile}

An Agile approach to developing the search application could distill
the use cases even further and shape the requirements to the rest
thereof later in the development process based on feedback and reacting
to changes. A similar approach would allow us to start with the smaller
domain model also discussed in section~\ref{appraisal} and allow it to grow
to the necessary size to need -- i.e. we can defer the decision of ``how big
should the domain model be?'' until we are at a point where we have more
information to answer such a question.

@@

The sequence diagrams seemed to provoke more debate of the merits of
returning rich information in a single response versus an AJAX-driven
approach (or some trade-off in between). Again, I would emphasise the
communication aspect of UML modelling and argue that encouraging such debate
is a successful application of UML, not a failure because a decision
has not been made between two designs at this early stage.

>>>>

\begin{abstract}
This paper combines Soft Systems Methodology and UML modelling to design a
high-level view of a search application that receives web content
from a variety of BBC content production systems and makes every item
then searchable by a BBC website visitor using the search feature.
\end{abstract}

@@

The purpose of this paper is to start the high-level design -- and perhaps
look at the lower levels of one or two aspects -- of a search application
specific to BBC content. The intent is to provide a consistent user interface
that allows the audience to find news articles, sport results,
TV catch-up, education resources and everything else the BBC produces.

@@

Checkland and Scoles \citep{checkland1990soft} decribed a \emph{Rich Picture} approach
for representing a problem situation early in SSM approaches.
Given the size and complexity of the
search system as a whole, a useful initial step is to create such an informal
representation of what is known about the problem. Figure~\ref{rich-picture}
shows what the authors know of the audience, search and most BBC online content areas.
Note that not all areas are covered and a strong emphasis is placed on TV
catch-up (e.g. via the iPlayer product). Radio catch-up is not mentioned
as it shares a lot of similarity with television in terms of use and any
differences are out of scope for this design.

@@

The problem of
a BBC-wide search application was predicted --
and has certainly shown itself -- to be a very large-scale problem, the
full extent of which cannot be covered in this paper. Thus it
is reasonable to conclude that the problem is not yet solved
at every level, but the high-level solutions are certainly promising.

@@

Overall, we have some promising, high-level models from which to
start making such more fine-grained decisions about the search
application. The use cases are likely sufficient for early iterations
or a \emph{Minimal Viable Product} \citep{junk2000dynamic} and
the behaviours capture the overall needs of the system. There is still
much scope for returning to our systems thinking and Soft Systems
Methodology to monitor the general model for Checkland's ``3 Es''
(efficacy, efficiency and effectiveness) \citep{checkland1990soft},
which is only briefly touched on in the authors' attempts to relate the
data model to the user's interaction with the system.

@@

Even the models that are presented in this paper do not paint the full
picture, but it could be argued that it is not their purpose to do so.
As stated at the end of Sect.~\ref{appraisal}, the use case diagram
provides a starting point that might be sufficient for an early
iteration of a project in an \emph{Agile} methodology. \citep{beck2001agile}

An Agile approach to developing the search application could distill
the use cases even further and shape the requirements to the rest
thereof later in the development process based on feedback and reacting
to changes. A similar approach would allow us to start with the smaller
domain model also discussed in Sect.~\ref{appraisal} and allow it to grow
to the necessary size to need -- i.e. we can defer the decision of ``how big
should the domain model be?'' until we are at a point where we have more
information to answer such a question.

@@

The sequence diagrams seemed to provoke more debate of the merits of
returning rich information in a single response versus an AJAX-driven
approach (or some trade-off in between). Again, the authors would emphasise the
communication aspect of UML modelling and argue that encouraging such debate
is a successful application of UML, not a failure because a decision
has not been made between two designs at this early stage.
